Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-02 prob.tex
prob.tex \section{Proofs} Adding footnote...

\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\qed\end{definition}

@@

Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
So 
\begin{eqnarray*}
 &  & \left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right|\\
 & = & \left|\left(f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|\\
 & = & \left|g_{f,\ket{0}}-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|
\end{eqnarray*}
\end{proof}

>>>>

\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{R}^{3}$,
$\sigma_{\ket{\psi},\theta}$ is rotation by $\theta$ about $\ket{\psi}$.\footnote{\yutsung{Write its matrix representation?}}\qed\end{definition}

@@

Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
So\footnote{\yutsung{Verify the details...}} 
\begin{eqnarray*}
 &  & \left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right|\\
 & = & \left|\left(f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|\\
 & = & \left|g_{f,\ket{0}}-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|
\end{eqnarray*}
\end{proof}
